\thesistitle

### 2019-07-30 sections/background.tex
Inheritance

>>>>

\subsection{Inheritance}
Object-Oriented programming languages use inheritance to model real-world relations between data concepts. Inheritance allows an object to inherit all functionality from another object. For instance, a ``Car'' object would inherit functionality and data from generalized concepts, such as ``Vehicle''. Using inheritance it is possible to reduce duplication, as multiple objects can inherit common functionality.

When looking at the inheritance structure of a program, we can get a deeper understanding of a programs' architecture. The use of inheritance to group common functionality and data is called ``Abstraction''. Duplication in source code can be a result of an inadequate use of abstraction. Because of that, refactoring code clones might require to create such abstractions of common functionality.

\subsection{Code Quality}

\subsubsection{Code Smells}

\subsubsection{Design Patterns}

\subsubsection{Code Quality Metrics}

\subsection{Java}
\todo{Describe the relevant parts of the Java ecosystem: interfaces, enumerations, annotations, etc.}

\subsubsection{Visibility}
